\text{Additive drift with tail bounds}

### 2021-10-14 article.tex
add def

\newcommand\setItemnumber[1]{\setcounter{enumi}{\numexpr#1-1\relax}}

@@

\begin{theorem}
    Suppose $X_t$ has a drift of at most $\varepsilon > 0$ and $(X_t - \varepsilon t)$ is $(c, \delta)$ - sub-Gaussian. Let \(X_0\) be \(a \in \mathbb{R}\) and let \(T\) be the first moment in time when \(X_t\) exceeds some \(b > a\). Then for all \(s \leq \frac{b - a}{2\varepsilon}\) we have

>>>>

\newcommand\setItemnumber[1]{\setcounter{enumi}{\numexpr#1-1\relax}}
\newtheorem*{definition}{Definition}
% \newtheorem{definition*}{Definition}

@@

\begin{definition}
    Process \(\{X_t\}_{t \geq 0}\) is called \underline{\((c, \delta)\)-sub-Gaussian} if for all \(t \geq 0\) and for all \(\lambda \in [0, \delta]\)

    \[E[e^{\lambda(X_{t + 1} - X_{t})}] \leq e^{\frac{\lambda^2 c}{2}}\]
\end{definition}

\begin{theorem}[Theorema 14 in \cite{Kotzing16}]
    Suppose $X_t$ has a drift of at most $\varepsilon > 0$ and $(X_t - \varepsilon t)$ is $(c, \delta)$-sub-Gaussian. Let \(X_0\) be \(a \in \mathbb{R}\) and let \(T\) be the first moment in time when \(X_t\) exceeds some \(b > a\). Then for all \(s \leq \frac{b - a}{2\varepsilon}\) we have
